---
title: "Sex & statistical power - simulations"
author: "Szymek Drobniak"
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    toc-location: left
    toc-depth: 2
    theme: simplex
    embed-resources: true
    code-fold: show
    code-tools: true
    number-sections: true
crossref: 
  fig-title: Figure     # (default is "Figure")
  tbl-title: Table     # (default is "Table")
  title-delim: —     # (default is ":")
  fig-prefix: Fig.   # (default is "Figure")
  tbl-prefix: Tab.    # (default is "Table")
editor_options: 
  chunk_output_type: console
---

```{r}
library(ggplot2)
library(pander)
library(emmeans)
library(tidyverse)
library(here)
```


Analysis preps (colours, options, auxiliary functions)

```{r}
cbb_palette <- c(
  "#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442",
  "#0072B2", "#D55E00", "#CC79A7"
)

## Avoid table wrapping
options(width = 800)
set.seed(999)

source(here("PhillipsKarpEtal_data/funs.r"))
```

Below results repeat simulations from the paper of *Phillips et al. (2018) PLoS Biol 21(6): e3002129*. Original results simplified by removing the post-hoc and the (pooled) t-test methods of analysing data. Generation of simulated data was modified to use a formal linear model defined as:

$$\mathbf{y} = \mathbf{X}\mathbf{b} + \mathbf{e}$$

with $\mathbf{b}=(\mu,\beta_{Treat},\beta_{Sex},\beta_{Treat:Sex})$ and $\mathbf{e} \sim \mathcal{N}(\mathbf{0}, \mathbf{s})$, with $\mathbf{s}=\mathbf{1}+\mathbf{X}_{Sex}\cdot\sqrt{\alpha}$ ($\alpha$ quantifies the amount of heteroscedasticity in sex variances, with $\sigma_{m}=\sigma_{f}\sqrt{1+\alpha}$, or male variance being $\alpha\cdot100\%$ greater than female). Regression coefficients ($\mathbf{b}$) are compatible with contrasts (sex/treatment effects) used in Phillips et al. (2023).

# Scenarios from Fig. 1

## From original paper

**Assuming homoscedasticity of sex variances**

::: {.panel-tabset}

## No sex eff, no ix

```{r}
#| code-fold: true

no_per_gp <- 5
variable_mean <- 1
variable_sd <- 0.5
treat_es <- 0
sex_es <- 0
female_es <- 0
male_es <- 0
treat_es2 <- treat_es
sex_es2 <- sex_es
ix_es2 <- 0
sex_sd <- 1

all_effs_sex_none <- rbind(
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.1, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.1, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.2, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.2, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.3, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.3, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.4, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.4, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.5, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.5, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.6, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.6, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.7, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.7, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.8, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.8, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.9, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.9, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 1, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 1, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    )
)

calc_power_sex_none <- all_effs_sex_none %>%
    filter(!Effect == "Residuals    ") %>%
    group_by(Effect, treat_es, male_es, sex_es, method) %>%
    summarise_all(.funs = list(~ sum(. < 0.05, na.rm = TRUE) / n())) %>%
    mutate(sex_eff_size = rep("none"))

calc_power_sex_none %>%
    ggplot(aes(x = treat_es, y = p_value, colour = Effect)) +
    geom_hline(yintercept = 0.8, linetype = "dashed") +
    geom_line(aes(group = Effect)) +
    theme_classic() +
    ylab("Power") + ylim(0, 1)
```

## Small sex eff, no ix

```{r}
#| code-fold: true


no_per_gp <- 5
variable_mean <- 1
variable_sd <- 0.5
treat_es <- 0
sex_es <- 0.5
female_es <- 0
male_es <- 0
treat_es2 <- treat_es
sex_es2 <- sex_es
ix_es2 <- 0
sex_sd <- 1

all_effs_sex_small <- rbind(
  p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.1, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.1, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.2, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.2, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.3, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.3, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.4, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.4, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.5, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.5, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.6, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.6, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.7, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.7, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.8, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.8, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.9, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.9, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 1, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 1, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    )
)

calc_power_sex_small <- all_effs_sex_small %>%
  filter(!Effect == "Residuals    ") %>%
  group_by(Effect, treat_es, male_es, sex_es, method) %>%
  summarise_all(.funs = list(~ sum(. < 0.05, na.rm = TRUE) / n())) %>%
  mutate(sex_eff_size = rep("small"))

calc_power_sex_small %>%
  ggplot(aes(x = treat_es, y = p_value, colour = Effect)) +
  geom_hline(yintercept = 0.8, linetype = "dashed") +
  geom_line(aes(group = Effect)) +
  theme_classic() +
  ylab("Power") + ylim(0, 1)

```


## Large sex eff, no ix

```{r}
#| code-fold: true


no_per_gp <- 5
variable_mean <- 1
variable_sd <- 0.5
treat_es <- 0
sex_es <- 1
female_es <- 0
male_es <- 0
treat_es2 <- treat_es
sex_es2 <- sex_es
ix_es2 <- 0
sex_sd <- 1

all_effs_sex_large <- rbind(
  p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.1, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.1, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.2, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.2, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.3, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.3, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.4, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.4, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.5, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.5, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.6, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.6, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.7, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.7, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.8, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.8, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.9, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.9, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 1, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 1, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    )
)

calc_power_sex_large <- all_effs_sex_large %>%
  filter(!Effect == "Residuals    ") %>%
  group_by(Effect, treat_es, male_es, sex_es, method) %>%
  summarise_all(.funs = list(~ sum(. < 0.05, na.rm = TRUE) / n())) %>%
  mutate(sex_eff_size = rep("large"))

calc_power_sex_large %>%
  ggplot(aes(x = treat_es, y = p_value, colour = Effect)) +
  geom_hline(yintercept = 0.8, linetype = "dashed") +
  geom_line(aes(group = Effect)) +
  theme_classic() +
  ylab("Power") + ylim(0, 1)

```
:::

Plots combining all scenarios from Fig. 1

```{r}
#| code-fold: true

all_sex_effs_sex_only <- rbind(calc_power_sex_none, calc_power_sex_small,
                               calc_power_sex_large)
all_sex_effs_sex_only <- as.data.frame(lapply(all_sex_effs_sex_only, unlist))

all_sex_effs_sex_only %>%
  filter(Effect %in% c("Treatment", "T-Test Treatment Eff")) %>%
  mutate(sex_eff_size = factor(sex_eff_size,
                               levels = c("none", "small", "large"))) %>%
  mutate(method = recode(method,
                         " Two Sample t-test" = "Pooled",
                         "ANOVA" = "Factorial")) %>%
  ggplot(aes(x = treat_es, y = p_value, colour = sex_eff_size,
             group = interaction(sex_eff_size, method))) +
  geom_hline(yintercept = 0.8, linetype = "dashed") +
  geom_line(aes(linetype = method)) +
  theme_classic() +
  ylab("Statistical power") +
  xlab("Main treatment effect") +
  scale_colour_manual(name = "Sex effect size", values = cbb_palette) +
  scale_linetype_discrete(name = "Stat method")  + ylim(0, 1)

all_sex_effs_sex_only %>%
  filter(!Effect %in% c("T-Test Treatment Eff")) %>%
  mutate(sex_eff_size = factor(sex_eff_size,
                               levels = c("none", "small", "large"))) %>%
  ggplot(aes(x = treat_es, y = p_value, colour = Effect,
             group = interaction(sex_eff_size, Effect))) +
  geom_hline(yintercept = 0.8, linetype = "dashed") +
  geom_line(aes(linetype = sex_eff_size)) +
  theme_classic() +
  ylab("Statistical power") +
  xlab("Main treatment effect") +
  scale_colour_manual(name = "Effect", values = cbb_palette) +
  scale_linetype_discrete(name = "Sex effect size") + ylim(0, 1)
```


## Heteroscedastic sex variances

We assume several scenarios with $\alpha$ ranging from 0 to 1, which relates to 50% or 100% increase in male variance, in relation to female variance.

**Low heteroscedasticity**

```{r}
alpha <- 0.5
```

::: {.panel-tabset}
## No sex eff, no ix

```{r}
#| code-fold: true

no_per_gp <- 5
variable_mean <- 1
variable_sd <- 0.5
treat_es <- 0
sex_es <- 0
female_es <- 0
male_es <- 0
treat_es2 <- treat_es
sex_es2 <- sex_es
ix_es2 <- 0
sex_sd <- 1+alpha

all_effs_sex_none <- rbind(
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.1, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.1, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.2, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.2, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.3, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.3, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.4, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.4, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.5, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.5, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.6, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.6, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.7, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.7, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.8, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.8, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.9, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.9, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 1, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 1, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    )
)

calc_power_sex_none <- all_effs_sex_none %>%
    filter(!Effect == "Residuals    ") %>%
    group_by(Effect, treat_es, male_es, sex_es, method) %>%
    summarise_all(.funs = list(~ sum(. < 0.05, na.rm = TRUE) / n())) %>%
    mutate(sex_eff_size = rep("none"))

calc_power_sex_none %>%
    ggplot(aes(x = treat_es, y = p_value, colour = Effect)) +
    geom_hline(yintercept = 0.8, linetype = "dashed") +
    geom_line(aes(group = Effect)) +
    theme_classic() +
    ylab("Power") + ylim(0, 1)
```

## Small sex eff, no ix

```{r}
#| code-fold: true


no_per_gp <- 5
variable_mean <- 1
variable_sd <- 0.5
treat_es <- 0
sex_es <- 0.5
female_es <- 0
male_es <- 0
treat_es2 <- treat_es
sex_es2 <- sex_es
ix_es2 <- 0
sex_sd <- 1+alpha

all_effs_sex_small <- rbind(
  p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.1, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.1, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.2, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.2, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.3, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.3, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.4, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.4, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.5, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.5, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.6, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.6, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.7, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.7, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.8, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.8, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.9, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.9, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 1, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 1, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    )
)

calc_power_sex_small <- all_effs_sex_small %>%
  filter(!Effect == "Residuals    ") %>%
  group_by(Effect, treat_es, male_es, sex_es, method) %>%
  summarise_all(.funs = list(~ sum(. < 0.05, na.rm = TRUE) / n())) %>%
  mutate(sex_eff_size = rep("small"))

calc_power_sex_small %>%
  ggplot(aes(x = treat_es, y = p_value, colour = Effect)) +
  geom_hline(yintercept = 0.8, linetype = "dashed") +
  geom_line(aes(group = Effect)) +
  theme_classic() +
  ylab("Power") + ylim(0, 1)

```


## Large sex eff, no ix

```{r}
#| code-fold: true


no_per_gp <- 5
variable_mean <- 1
variable_sd <- 0.5
treat_es <- 0
sex_es <- 1
female_es <- 0
male_es <- 0
treat_es2 <- treat_es
sex_es2 <- sex_es
ix_es2 <- 0
sex_sd <- 1+alpha

all_effs_sex_large <- rbind(
  p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.1, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.1, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.2, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.2, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.3, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.3, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.4, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.4, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.5, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.5, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.6, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.6, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.7, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.7, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.8, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.8, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.9, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.9, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 1, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 1, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    )
)

calc_power_sex_large <- all_effs_sex_large %>%
  filter(!Effect == "Residuals    ") %>%
  group_by(Effect, treat_es, male_es, sex_es, method) %>%
  summarise_all(.funs = list(~ sum(. < 0.05, na.rm = TRUE) / n())) %>%
  mutate(sex_eff_size = rep("large"))

calc_power_sex_large %>%
  ggplot(aes(x = treat_es, y = p_value, colour = Effect)) +
  geom_hline(yintercept = 0.8, linetype = "dashed") +
  geom_line(aes(group = Effect)) +
  theme_classic() +
  ylab("Power") + ylim(0, 1)

```
:::


**Large heteroscedasticity**

```{r}
alpha <- 1
```

::: {.panel-tabset}
## No sex eff, no ix

```{r}
#| code-fold: true

no_per_gp <- 5
variable_mean <- 1
variable_sd <- 0.5
treat_es <- 0
sex_es <- 0
female_es <- 0
male_es <- 0
treat_es2 <- treat_es
sex_es2 <- sex_es
ix_es2 <- 0
sex_sd <- 1+alpha

all_effs_sex_none <- rbind(
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.1, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.1, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.2, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.2, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.3, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.3, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.4, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.4, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.5, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.5, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.6, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.6, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.7, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.7, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.8, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.8, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.9, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.9, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 1, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 1, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    )
)

calc_power_sex_none <- all_effs_sex_none %>%
    filter(!Effect == "Residuals    ") %>%
    group_by(Effect, treat_es, male_es, sex_es, method) %>%
    summarise_all(.funs = list(~ sum(. < 0.05, na.rm = TRUE) / n())) %>%
    mutate(sex_eff_size = rep("none"))

calc_power_sex_none %>%
    ggplot(aes(x = treat_es, y = p_value, colour = Effect)) +
    geom_hline(yintercept = 0.8, linetype = "dashed") +
    geom_line(aes(group = Effect)) +
    theme_classic() +
    ylab("Power") + ylim(0, 1)
```

## Small sex eff, no ix

```{r}
#| code-fold: true


no_per_gp <- 5
variable_mean <- 1
variable_sd <- 0.5
treat_es <- 0
sex_es <- 0.5
female_es <- 0
male_es <- 0
treat_es2 <- treat_es
sex_es2 <- sex_es
ix_es2 <- 0
sex_sd <- 1+alpha

all_effs_sex_small <- rbind(
  p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.1, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.1, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.2, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.2, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.3, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.3, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.4, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.4, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.5, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.5, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.6, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.6, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.7, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.7, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.8, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.8, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.9, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.9, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 1, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 1, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    )
)

calc_power_sex_small <- all_effs_sex_small %>%
  filter(!Effect == "Residuals    ") %>%
  group_by(Effect, treat_es, male_es, sex_es, method) %>%
  summarise_all(.funs = list(~ sum(. < 0.05, na.rm = TRUE) / n())) %>%
  mutate(sex_eff_size = rep("small"))

calc_power_sex_small %>%
  ggplot(aes(x = treat_es, y = p_value, colour = Effect)) +
  geom_hline(yintercept = 0.8, linetype = "dashed") +
  geom_line(aes(group = Effect)) +
  theme_classic() +
  ylab("Power") + ylim(0, 1)

```


## Large sex eff, no ix

```{r}
#| code-fold: true


no_per_gp <- 5
variable_mean <- 1
variable_sd <- 0.5
treat_es <- 0
sex_es <- 1
female_es <- 0
male_es <- 0
treat_es2 <- treat_es
sex_es2 <- sex_es
ix_es2 <- 0
sex_sd <- 1+alpha

all_effs_sex_large <- rbind(
  p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.1, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.1, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.2, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.2, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.3, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.3, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.4, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.4, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.5, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.5, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.6, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.6, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.7, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.7, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.8, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.8, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 0.9, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 0.9, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    ),
    p_value_interaction_crossed(
        n_rep = 1000, no_per_gp = no_per_gp, variable_mean = variable_mean,
        variable_sd = variable_sd, treat_es = 1, sex_es = sex_es,
        male_es = male_es, female_es = female_es,
        treat_es2 = 1, sex_es2 = sex_es2, ix_es2 = ix_es2, sex_sd = sex_sd
    )
)

calc_power_sex_large <- all_effs_sex_large %>%
  filter(!Effect == "Residuals    ") %>%
  group_by(Effect, treat_es, male_es, sex_es, method) %>%
  summarise_all(.funs = list(~ sum(. < 0.05, na.rm = TRUE) / n())) %>%
  mutate(sex_eff_size = rep("large"))

calc_power_sex_large %>%
  ggplot(aes(x = treat_es, y = p_value, colour = Effect)) +
  geom_hline(yintercept = 0.8, linetype = "dashed") +
  geom_line(aes(group = Effect)) +
  theme_classic() +
  ylab("Power") + ylim(0, 1)

```
:::

It should be of note that evolutionary biology has seen heteroscedasticities exceeding 100% in variance ration between sexes.